Inferring neural networks from fluorescent calcium imaging using partial correlation and sample weighting

### 2014-05-30 article.tex
add todo
Reformulate probability part

% introduce the notion of dependance/independance
From a probabilistic point of view, the inference of the undirected network
can be formulated as inferring the conditional independence between neurons
$i$ and $j$ conditionally to all other neurons
$i \perp j | 1,\ldots,p \backslash \left\{i, j\right\}$. Note that
the unconditional independence $i \perp j$ between  $i$ and $j$ doesn't allow to
infer the graph due to indirect effect. For instance if neurons $A, B, C$ have
the connectivity graph $A \rightarrow B \rightarrow C$, then we have the
dependence $A \not\perp C$ and the conditional independence $A \perp C | B$.

>>>>

% introduce the notion of dependence / independence
% TODO add a more formal definition of independence.
From a probabilistic point of view, the inference of the undirected network
can be formulated as inferring conditional dependences and
independences. Each neuron signal $i$ is a random continuous variable $X_i$,
which follows a probability density function $p_\mathcal{X_i}(x_i)$.
Two neurons $X_i$, $X_j$ will be said conditionally independent
$X_i \perp X_j | X_1,\ldots,X_p \backslash \left\{X_i, X_j\right\}$ to all
others neuron if
\begin{align*}
&p_{X_i, X_j | X_1,\ldots,X_p \backslash \left\{X_i, X_j\right\}}
    (x_i, x_j | x_1,\ldots,x_p \backslash \left\{x_i, x_j\right\}) \\
=&p_{X_i | X_1,\ldots,X_p \backslash \left\{X_i, X_j\right\}}
    (x_i | x_1,\ldots,x_p \backslash \left\{x_i, x_j\right\})
p_{X_j | X_1,\ldots,X_p \backslash \left\{X_i, X_j\right\}}
    (x_j | x_1,\ldots,x_p \backslash \left\{x_i, x_j\right\})
\end{align*}
for all real numbers $x_1,\ldots,x_p $ such that
$p_{X_1,\ldots,X_p \backslash \left\{X_i, X_j\right\}}
 (x_1,\ldots,x_p \backslash \left\{x_i, x_j\right\}) > 0$.
Thus if $X_i \not\perp X_j | X_1,\ldots,X_p \backslash \left\{X_i, X_j\right\}$,
then we have the edge $i-j$ in the undirected graph.
